\input{header}

\title{RPGG RANDOM Design Experience, 2022}
\begin{document}
\mainmatter
\subsection{RPG Geek RANDOM Design 2022}
\DndDropCapLine{R}{andom tables} are the primordial ooze from which all games
originate. The Geeks of
\href{https://rpggeek.com/}{RPGG}
present the results of their enthusiastic enumeration of eclectic effects - AKA
the
\href{https://rpggeek.com/thread/2942480/2022-r-n-d-o-m-design-experience}{RPGG
R-A-N-D-O-M Design Experience} of 2022.

We did this in 2016 and it worked. Oops, we did it again in 2017. Then we forgot
about it for 2 years. Then we did 2020. And it worked. As Ned Flanders
might say:
\begin{DndReadAloud}
Ding dang diddly! If we did it once, we can do it again!
\end{DndReadAloud}

The theme this year was \emph{\textbf{events that I don't want to go through all the
trouble to run}}.
\vfill

\subsection{Tables}

% Use this line if you want the PDF to be fully data-driven
% \input{tex/all_tables}

% Otherwise this is the current manually-paginated version. Needs updating if
% new tables are added, or when tables change length.
\input{tex/001_events_I_dont_want_to_run.tex}
\vfill\newpage
\input{tex/034_animals.tex}
\input{tex/017_beasts.tex}
\vfill\newpage
\input{tex/039_body_parts.tex}
\input{tex/025_books.tex}
\vfill\newpage
\input{tex/022_building_materials.tex}
\input{tex/032_colors.tex}
\vfill\newpage
\input{tex/023_conflicts.tex}
\input{tex/031_dances.tex}
\vfill\newpage
\input{tex/036_deities.tex}
\input{tex/033_directions.tex}
\vfill\newpage
\input{tex/020_distances.tex}
\input{tex/002_factions.tex}
\vfill\newpage
\input{tex/016_faekind.tex}
\input{tex/030_flowers.tex}
\vfill\newpage
\input{tex/013_forbidden_things.tex}
\input{tex/043_games.tex}
\input{tex/015_goblinoid.tex}
\vfill\newpage
\input{tex/038_icky_things.tex}
\input{tex/003_leaders.tex}
\vfill\newpage
\input{tex/010_locations.tex}
\input{tex/041_meals.tex}
\vfill\newpage
\input{tex/011_monsters.tex}
\input{tex/029_occupational_duties.tex}
\vfill\newpage
\input{tex/009_persons.tex}
\input{tex/040_pets.tex}
\vfill\newpage
\input{tex/004_planets.tex}
\input{tex/035_pokey_things.tex}
\vfill\newpage
\input{tex/042_professions.tex}
\input{tex/008_petty_things.tex}
\vfill\newpage
\input{tex/018_ranks.tex}
\input{tex/026_relatives.tex}
\vfill\newpage
\input{tex/006_size.tex}
\input{tex/007_spacecraft.tex}
\vfill\newpage
\input{tex/005_stars.tex}
\input{tex/012_streets.tex}
\vfill\newpage
\input{tex/037_structures.tex}
\input{tex/021_temperaments.tex}
\vfill\newpage
\input{tex/024_temporal.tex}
\input{tex/014_undead.tex}
\vfill\newpage
\input{tex/027_evil_adjectives.tex}
\input{tex/028_good_adjectives.tex}
\vfill\newpage
\input{tex/019_swampy_adjective.tex}

\vfill\pagebreak
\section{Contributors}
The Un-random table of glorious contributors.
\begin{DndTable}[]{c X}
    1 & TheGoodGuy \\
    2 & Adularia25 \\
    3 & jajsxa \\
    4 & pikkusiili2000 \\
    5 & taen \\
    6 & ThroughTheDeckGlass \\
    7 & paulidale \\
    8 & ctimmins \\
    9 & SeaofStars \\
    10 & JugglinDan \\
    11 & Dragontrainer \\
    12 & sbszine \\
    13 & Dutys\_Fist \\
    14 & robbbbbb \\
    15 & QuaidSlauson \\
    16 & Shardra \\
    17 & Chadnorth \\
    18 & sdonohue \\
    19 & dragontrainer \\
    20 & Steerpike.Instance \\
    21 & chadnorth \\
    22 & Volfield \\
\end{DndTable}


\end{document}